\section{Contributions}
\label{section:contributions}

There are a number of significant contributions from this thesis that move toward a formal implementation of the Information Dynamics of Thinking theory, which up until now, and not counting other IDyOT-like systems \citep{forth2016entraining}, was almost entirely a theoretical proposition.  Specifically, a significant portion of Chapter 3: Theory \& Implementation is work contributed by the author, though of course with guidance from the promoter and advisor, Prof. Dr. Dr. Geraint Wiggins.  A short review of specific contributions is presented in the following paragraph.  

Tensor rank promotion (section \ref{section:tensor-rank-promotion}) and element-wise independence (section \ref{section:elementwise-independence}) of the tensors produced in the abstraction process, though falling directly from the theory, were identified by the author. Though content sparsity was known prior in the theory, the problem of signal sparsity (section \ref{section:signal-sparsity}), in conjunction with the necessity for equal-shaped tensors falling from Hilbert space isopmorphism (section \ref{section:hilbert-space-isomorphism}) led to the need for interpolation (section \ref{section:interpolation}) and its proposed solution in regression sampling (section \ref{section:regression-sampling}).  In addition, the adaptive categorization (section \ref{section:adaptive-categories}) technique expanded on the idea of an inclusion radius and made it adaptive to the constituents of the category.

Beyond these theoretical contributions, this is the first, albeit limited, realized implementation of IDyOT that utilizes all three main processes: abstraction, segmentation, and categorization. As seen in the results, this is the first empirical analysis that spectral representations of meaning in the context of IDyOT, at least in human speech, can produce identifiable representations in a hierarchical manner.  This highly novel and general approach to perceptual representation could have far-reaching consequences, but here was the first empirical result that the whole theory might be viable.
